### 2015-05-03 draft.tex
..

\documentclass[12pt]{article}
\usepackage[latin1]{inputenc}

@@

\subsection*{A.P.I.}

\begin{figure}
  \begin{lstlisting}
(* a standard packet field *)
type field = IpSrc | IpDst

@@

(* forwarding decision can deliver, drop, forward, multicast *)
type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
	| Ctrl

(* abstract packet type *)
type packet

@@

(* in_range p f r returns true if the value of field f of packet p is in range r, and false otherwise *)
val in_range: packet -> field -> range -> bool
\end{lstlisting}

\caption{Signature of the packet and range-branching portion of the API}
\end{figure}

@@

(* test if a packet's fields are in a relation *)
val in_relation: packet -> field list -> relation -> bool
\end{lstlisting}

@@

(* Print the policy to stdout *)
val print_policy: policy -> unit
  \end{lstlisting}
  \caption{Signature of the interactive portion of the API}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}

@@

\subsection*{A.P.I.}
In our model, algorithmic policies interact with packets through A.P.I function calls before returning a forwarding decision. We include in Figure~\ref{fig:range_api} the core of our \lstinline|API|.

\lstinline|field| enumerates the different fields of a packet. It can be extended to represent more fields of a packet's header. Associated with \lstinline|field| are \lstinline|range|s, possible values taken by a certain packet's field, within a given minimum value \lstinline|min_value| and maximum value \lstinline|max_value|. \lstinline|range| consists of list of integer pairs, representing a collection of intervals whose union correspond to the range of values of a packet. For simplicity, we consider integer fields here, but this could be extended, for example, to IP prefix, boolean flags, etc.

\lstinline|forwarding_decision| enumerates the different forwarding decision which can be returned by an algorithmic policy. \lstinline|Deliver| forwards the packet to its destination, \lstinline|Drop| drops the packet, \lstinline|ForwardTo i| forwards the packet to a constant location \lstinline|i| and \lstinline|Multicast fd1 fd2| duplicates the packet and handles each according to \lstinline|fd1| and \lstinline|fd2| respectively.

\begin{figure}
  \begin{lstlisting}
(* abstract packet type *)
type packet

(* a standard packet field *)
type field = IpSrc | IpDst

@@

@@

(* forwarding decision can deliver, drop, forward, multicast *)
type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
	| Ctrl (* TODO: should not expose this *)

(* in_range p f r returns true if the value of field f of packet p is in range r, and false otherwise *)
val in_range: packet -> field -> range -> bool
\end{lstlisting}
\label{fig:range_api}
\caption{Signature of the packet and range-branching portion of the API}
\end{figure}

@@

(* test if a packet's fields are in a relation *)
val in_relation: packet -> field list -> relation -> bool
\end{lstlisting}
\label{fig:rel_api}
\caption{Signature of the relation portion of the API}
\end{figure}

@@

(* Print the policy to stdout *)
val print_policy: policy -> unit
  \end{lstlisting}
  \label{fig:build_api}
  \caption{Signature of the interactive portion of the API}
\end{figure}
